Demographic data validation

### 2021-08-09 doc/validate_data.Rmd

```{r processed}
create_agent(
  model_data,
  actions = action_levels(warn_at = 1, stop_at = 0.2)
) %>% 
  col_is_character(vars(code_notes)) %>% 
  col_is_factor(vars(ranch, bdffp_reserve_no, plot, habitat, ha_id_number)) %>% 
  col_is_numeric(vars(ht, ht_prev, size, size_prev, log_size, log_size_prev)) %>%
  col_is_integer(vars(year, shts, shts_prev, infl_num, surv, flwr)) %>% 
  col_vals_in_set(vars(surv, flwr), c(0,1, NA)) %>% 
  col_vals_in_set(vars(habitat), c("1-ha", "CF", "10-ha")) %>% 
  col_vals_between(vars(shts, shts_prev), 1, 20, na_pass = TRUE) %>% 
  col_vals_between(vars(ht, ht_prev), 0, 200, na_pass = TRUE) %>% 
  rows_distinct() %>% 
  interrogate()
```

>>>>

```{r processed}
create_agent(
  model_data,
  actions = action_levels(warn_at = 1, stop_at = 0.2)
) %>% 
  col_is_character(vars(code_notes)) %>% 
  col_is_factor(vars(ranch, bdffp_reserve_no, plot, habitat, ha_id_number)) %>% 
  col_is_numeric(vars(ht, ht_prev, size, size_prev, log_size, log_size_prev)) %>%
  col_is_integer(vars(year, shts, shts_prev, infl, infl_prev, surv, flwr, flwr_prev)) %>% 
  col_vals_in_set(vars(surv, flwr), c(0,1, NA)) %>% 
  col_vals_in_set(vars(habitat), c("1-ha", "CF", "10-ha")) %>% 
  col_vals_between(vars(shts, shts_prev), 1, 20, na_pass = TRUE) %>% 
  col_vals_between(vars(ht, ht_prev), 0, 200, na_pass = TRUE) %>% 
  rows_distinct() %>% 
  interrogate()
```
